
---
title: "A3 Dictionaries and metadata on COVID-19 resources"
author: 'Vincent J. Carey, stvjc at channing.harvard.edu'
date: '`r Sys.Date()`'
output:
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{A3 Dictionaries and metadata on COVID-19 resources}
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

Data representation often involves various levels
of explicitness.  A "variable name" is a short
token that can be used in programming to
refer to some quantity or outcome or event of interest.

A data dictionary maps variable names to more
explicit definitions of quantities, outcomes, events,
and may include more information on context of
measurement.

# Example: CDC's data dictionary on vaccination trends

We have included a version of a CDC data dictionary.
It is published as a multisheet Excel workbook.

Code to retrieve the names of the sheets, using `excel_sheets`:
```{r lkdd1, message=FALSE}
library(readxl)
pa = system.file("cdc/VACCDataDictionary_v36_12082022.xlsx", package="teachCovidData")
shn = excel_sheets(pa)
shn
```

The first sheet is an overview:
```{r lkdd2, message=FALSE}
p1 = read_xlsx(pa, 1)
knitr::kable(head(as.data.frame(p1)))
```

We process all sheets using `process_datadict`:
```{r lkdd3,message=FALSE}
library(teachCovidData)
pd = process_datadict(pa)
```

An interactive view of the second sheet:
```{r lkdd4,message=FALSE}
library(DT)
datatable(pd[[2]])
```

To survey the dictionary in R, use `datadict_app(pd)` after
performing the calculations above, or with `example(datadict_app)`.
