
---
title: "B1 US Infection reports: timing"
author: 'Vincent J. Carey, stvjc at channing.harvard.edu'
date: '`r Sys.Date()`'
output:
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{B1 US Infection reports: timing}
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

In this section we will work with time series of reports 
of new cases of COVID-19 infection.

Another time series resource of interest records
date, place and assigned cause of
[COVID-19 related deaths](https://data.cdc.gov/NCHS/Provisional-COVID-19-Deaths-by-Sex-and-Age/9bhg-hcku).
At this time we will not be analyzing this data.

# A snapshot of data from "USAfacts"

The `usafacts_confirmed` function produces
a table with rows corresponding to US counties
and columns corresponding to dates.  Entries
of the table are counts of new COVID-19 cases.

Here's a quick look at the table:
```{r lkcc,message=FALSE}
library(teachCovidData)
cc = usafacts_confirmed() # confirmed cases by county
library(dplyr)
MSdata = cc |> filter(State=="MS")
head(MSdata[,1:10])
tail(names(MSdata)) # why
```

We have to massage the column names to
simplify programming with reocrd dates.

```{r dodates}
dates = lubridate::as_date(names(MSdata[-c(1:4)]))
cumulative = apply(MSdata[,-c(1:4)],2,sum)
head(cumulative)
```

We can now visualize cumulative case counts:

```{r docum,message=FALSE}
library(ggplot2)
mydf1 = data.frame(cumulative, dates)
ggplot(mydf1, aes(x=dates, y=cumulative)) + geom_point() + ggtitle("Cumulative Confirmed Covid cases in MS")
```

"Incidence" refers to the rate at which new cases arise,
frequently reported as number of cases (in a given
period of time) per 100000 individuals at risk at the start of the interval.

We use differences in cumulative counts to visualize
time and size of outbreaks.
```{r lki}
incid = diff(cumulative)
ndate = dates[-1]
mydf2 = data.frame(incid, ndate)
ggplot(mydf2, aes(x=ndate, y=incid)) + geom_point() + ggtitle("New daily cases in MS")
```

