---
title: "teachCovidData - overview"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{01 teachCovidData - overview}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup, echo=FALSE, results="hide"}
suppressMessages({
suppressPackageStartupMessages({
library(teachCovidData)
library(ggplot2)
})
})
```

# Introduction

We will assemble some data and analyses of COVID-19 data
using R.

## Installation

You can install this package in R with the following steps.

- ensure that you are using R 4.1 or later
- `install.packages("BiocManager")`
- `BiocManager::install(c("remotes", "vjcitn/teachCovidData"))`



# Basic data resource

```{r lk0}
library(teachCovidData)
dat = usafacts_confirmed()
dat[1:5,1:6]
```

# Examining new daily case counts by state

```{r lk1}
library(ggplot2)
ncms = new_cases_state("MS")
plot(ncms)
```

```{r lk2}
nn = new_cases_state("VT")
plot(nn)
```

Use dplyr to filter by date.
```{r lk3}
library(dplyr)
nnn = nn |> filter(date > "2021-01-01" & date < "2021-06-01")
plot(nnn)
```

Make the comparable plot for MS.

